There once was a grid at ol' Carkeek

### 2016-05-13 Manuscript/v0.0/carkeek_grid.tex
formal incorporation of life history data

>>>>

The vast majority (97.6\%) of sequences and OTUs (96.9\%) were matched to organisms that have high potential for dispersal at either the gamete, larval, or adult stage. 
Of the 6 OTUs with limited dispersal, only 2 occurred in more than two samples. 
These were assigned to \textit{Cymatogaster aggregata}, a viviparous nearshore fish with internal fertilization, and \textit{Cupolaconcha meroclista}, a sessile marine gastropod with internal fertilization and short larval dispersal (CITE???). 
Thus, we are unable to compare the patterns of dispersion for varying life history categories.
